%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 
%% Acknowledgements for your thesis in default document language
%% 

\cleardoubleoddpage%  Make sure to start acknowledgements on a new odd page
\includeChapterImage
\begin{acks*}
%\chapter*{Recognition and Thanks}

"One is too small a number to achieve greatness. No accomplishment of real value has ever been achieved by a human working alone."

\hfill - John C. Maxwell


With this in mind, I would like to express my sincere gratitude to everyone who has contributed to completing my work. 
Without their support, guidance, and encouragement, I would not have been able to finish it.
First, I would like to thank Prof. Christian Diskus and Dr. Florian Starzer for making this exciting project possible. 
Their vast effort in supervising my work was fundamental, and their knowledge has been invaluable in shaping the outcome.
I extend my profound gratitude to Dipl-Ing. Roland Vuketich for his consistent encouragement and unwavering support, 
which have served as a profound source of motivation throughout the duration of the whole project.
Furthermore, I wish to acknowledge and express my gratitude to Dipl-Ing. Dominik Breuer-Friedl for his substantial contributions and stimulating discussions. 
His remarkable expertise and insightful perspectives have significantly enriched the project.
I also wish to offer my heartfelt thanks to Dr. Patrick Hoelzl for his mentorship and enduring support during the course of my bachelor's work. 
His valuable guidance and willingness to share knowledge have been deeply appreciated.
Additionally, I express my gratitude to Dr. Thomas Faseth and Dr. Andreas Och, Dipl-Ing. Dominik Lungenschmied and Stefan Seeber for their dedicated support and active engagement throughout this endeavor.

I would also like to thank my family for their support and encouragement throughout my studies. 
Their love and belief in me were a constant source of strength, and I am truly grateful for everything they have done for me.
Finally, I express my appreciation and love to my girlfriend, Magdalena Stadlmair. 
Her support and encouragement have been the driving force behind my success. 
She is the most wonderful person in my life, and I am grateful every day for her love and support.

I would like to extend my heartfelt thanks to all others who have contributed to my work and helped me in the process, 
their support has been invaluable, and I am truly grateful for everything they have done. 
\end{acks*}
%
%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

